Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
- shortened FPDIT calculation text

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding a synchronous instant of
		this system (an instant at which all tasks release a job simultaneously), but
		with weaker constraints. That is, the FPDIT is an instant after the last
		deadline of all tasks, but before the next arrival time of all tasks. Finding
		a synchronous instant is equivalent to finding a solution $t$ for the
		following set of constraints :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		which is very similar to an instance of the Chinese Remainder Problem (CRP). It
		is not possible to directly use a solver for the CRP (such as Gauss's
		algorithm \cite{gauss1965disquisitiones}) as in a task system, $T_i$ values could have common factors.
		However, the instance can be modified (each constraint with a non-prime period can be split into powers of primes
		without changing the solution if there is one) in order to make the problem
		solvable through applying a solution for the CRP. \\

		Now that we have a solver for the problem of finding a synchronous instant, we
		actually also have a solver for finding the FPDIT. The problem of finding the
		first DIT is the same as finding all the possible DIT then taking the minimum.
		Each of those DIT corresponds to a unique combination of $a_i$ values (one
		for each task). Finding one of such DIT is the same problem as finding a
		synchronous instant :
		\[
			\left\{
			\begin{array}{l}
				t \geqslant O_i + a_i \: \forall \: \tau_i \in \tau \\
				t \equiv O_i \; (mod \; T_i) \: \forall \: \tau_i \in \tau \\
			\end{array}
			\right.
		\]
		all DITs can be found by solving the equivalent CRP problem for all
		combinations of $a_i$ values. This is however very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks.\\

		A better method for finding the FPDIT consists in splitting Gauss's algorithm
		into two separate parts. The global structure is simply a sum of factors, each
		term being dependent on which $a_i$ value is chosen. A major speedup can
		be achieved by first computing all possible terms for each task (only one
		modular inverse must be computed per task that way) then creating all possible DIT values
		by summing the terms in all possible ways. The number of results is still
		exponential in the number of tasks, but the only operation that is repeated
		exponentially many times is now a sum.

>>>>

	\subsection{Solving the modular system}
		Finding the FPDIT of a system is similar to finding at least one synchronous
		instant (an instant at which all tasks release a job simultaneously) out of a
		collection of systems with different offsets. The existence conditions can
		directly be used to calculate the value of the FPDIT (if there is one),
		because for a given set of $a_i$ values they are very similar to an instance
		of the Chinese Remainder Problem (CRP), which is easily solved using Gauss's
		CRP solving method for non-coprime $T_i$ \cite{gauss1965disquisitiones}. \\

		However this is very inefficient as there are exponentially many different
		combinations of $a_i$ values in the number of tasks. A better method for finding the FPDIT consists in splitting Gauss's
		algorithm into two separate parts. Its global structure is simply a sum of
		factors, each term being dependent on which $a_i$ value is chosen. A major speedup can
		be achieved by first computing all possible terms for each task then creating all
		possible DIT values by summing the terms in all possible ways. The number of results is still
		exponential in the number of tasks, but the only operation that is repeated
		exponentially many times is now a sum.
